### 2015-04-11 abstract.tex
Update outline.

The largest HPC centers spend considerable time supporting software configurations for thousands of users, but the complexity of software is quickly outpacing the capabilities of existing management tools. Modern HPC applications may require specific versions of many dependency libraries, and they must build with many compilers and MPI versions. The configuration space is exponential in size, and it is infeasible to maintain a single software stack for all users at a site. Existing tools are not sufficient to manage this complexity. We present Spack, a novel package management tool that allows users to build software configurations on demand. Spack provides a novel, recursive specification syntax, and it allows arbitrarily many software and dependency combinations to coexist on the same system. Spack's build mechanism ensures that each package can find its dependencies, regardless of a user's runtime environment settings. Spack brings order to the complexity of HPC software installation management.

>>>>

Large HPC centers spend considerable time supporting software for thousands of users, but the complexity of HPC software is quickly outpacing the capabilities of existing management tools. Scientific applications require specific versions of many compilers, MPI versions, and dependency libraries.  This makes a single software stack infeasible, but managing many configurations is difficult because the configuration space is exponential in size.
%
Spack is a package management tool used at Lawrence Livermore National Laboratory (LLNL) to manage software complexity. It allows many different software configurations to build on demand and to coexist on the same system. Spack provides a novel, recursive specification syntax to manage combinatoric builds of packages and dependencies.  It ensures that installed packages find their runtime dependencies, {\it regardless of the environment}. We show through real-world use cases that Spack supports a diverse and demanding user base, bringing order to the chaos of HPC software management.

### 2015-04-11 implementation.tex
Update outline.

>>>>

\begin{verbatim}
module disadvantages:
	- lmod solves a lot of problems
	- not on all systems
		- users often run from just a path.
		- not guaranteed that LD_LIBRARY_PATH, etc will
		  be set correctly.

- Lmod assumes build & submit environment must match
	- users often have NO IDEA what environment a package
	  was built with
	- multiple apps may be built with different stacks
	- combining them in a workflow is difficult with modules
		(need to know right incantation)

	- TACC implements a rather complicated mapping back to
	    the build env (Lmod CheckExec)

- Spack solves the matrix problem mentioned in the Lmod
    presentation (slide 98)
	- hierarchy is nasty -- every branch represents a
	  greedy choice
	- might NEED a specific version of ONE dependency
	  that is not supported in the tree
	  => SPACK!

- libmesh
	- boost, petsc, trilinos, grvy, etc.
\end{verbatim}

### 2015-04-11 introduction.tex
Updated build.
Update outline.

>>>>

- Build space on HPC machines is exponential
	- each new variable multiplies number of build combinations
	- complicated by the ABI.
	- often need a new version on demand
		- cannot just build it.

	- need tools that can sample space.

	- users cannot navigate space, and cumbersome to specify all details
	- users often only care about a subset of constraints and just want things
		built.
	- users need to run code again later, but don't remember complex module
		setup -- dynamic settings lead to user support calls and difficulties.

	- install procedure is different between users and admins
		- duplicated effort
		- need reusable package file.
